### 2019-05-07 sections/language.tex
refer to Haskell impl instead of Idris

Tasks can be annotated with additional information.
The system can use this information in various ways.
Possible use cases are labels for the user interface, resource consumption information for static resource analysis, or messages for automatic end-user feedback.
Annotations are not covered in this paper.
Our Idris implementation of \TOPHAT supports annotating tasks with user \ID{}s, so that individual tasks in a large workflow can be assigned to different users.
These annotations are used to filter the user interfaces for each user so that they can only see their part of the workflow.

>>>>

Tasks can be annotated with additional information.
The system can use this information in various ways.
Possible use cases are labels for the user interface, resource consumption information for static resource analysis, or messages for automatic end-user feedback.
Annotations are not covered in this paper.
Our Haskell implementation of \TOPHAT supports annotating tasks with user \ID{}s, so that individual tasks in a large workflow can be assigned to different users.
These annotations are used to filter the user interfaces for each user so that they can only see their part of the workflow.
